Invasive chameleons released from predation display more conspicuous colours

### 2022-01-23 supp_Nature.Rmd
Removed ms refs as they are not longer merged. Not sure why formatting for Table S6 is not working.

[@RN15ms;@RN7ms;@RN11ms;@RN6ms;@RN22ms;@RN2ms;@RN25ms;@RN8ms;@RN3ms;@RN1ms;@RN13ms;@RN18ms;@RN9ms;@RN12ms;@RN26ms;@RN24ms;@RN19ms;@RN5ms;@Measey2014ms;@RN20ms;@RN14ms;@RN4ms;@RN10ms]

@@

  # Table
 Tab_S6 <- flextable(final_S6) %>%  table_styleS6() %>% fit_to_width(max_width = 7)
 Tab_S6

```
# Additional Supplemental Results
## Body regions are perceived differently by predators but exhibited similar effect sizes

>>>>

@@

  # Table
 Tab_S6 <- flextable(final_S6) %>%  table_styleS6() %>% fit_to_width(max_width = 7)
 Tab_S6
```

# Additional Supplemental Results
## Body regions are perceived differently by predators but exhibited similar effect sizes
